\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-10 paper_resources/doc/paper.tex
New CD plots generated

@@

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there.

>>>>

%time-avg-noise0.0.eps

\begin{figure}[!ht]

	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.0.eps}
		\caption{No noise}
		\label{fig:noNoise-time}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\textwidth}

		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.001.eps}
		\caption{Level of noise equal to 0.001}
		\label{fig:noise0.001-time}
	\end{subfigure}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[  width=220pt,height=150pt]{plots/time-avg-noise0.01.eps}
		\caption{Level of noise equal to 0.01.}
		\label{fig:noise0.01-time}
	\end{subfigure}
	\caption{Average runtimes on the instance problems where the exact solution has  been reached (considered only those algorithms whose the exact percentage is at least 5\% of all runs).}
	\label{fig:time-avg-exact-noise}
\end{figure}

In Figure~\ref{fig:time-avg-exact-noise}, average runtimes of the algorithms on those instance problems from the both ground-truth benchmarks for which the exact model has  been found are compared. Those algorithms which obtained an exact percentage of at least 5\% (considering all 1300 runs) are considered as relevant here and therefore included into comparisons.  The results are grouped varying different (three) levels of noise, each presented by a plot, where the algorithms are labelled on $x$-axis, while their average runtimes are shown on $y$-axis. The following conclusions are drawn from here.

\begin{itemize}
	\item \fxnote{TODO...}
\end{itemize}

@@

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained exact percentages of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there. \fxnote{Marko: update of the content needed.}
